Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Pass of body up to Sec 6

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\Lcvx}{\mathcal{L}^{\text{cvx}}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
Depending on the data distribution, these inconsistent surrogates may actually yield high misprediction rates. \jessiet{Clean this up.}
%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question.

For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.\jessie{Some of this repetitive}

@@

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings. 
Reducing surrogate prediction dimension which maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\jessie{cite}).

\paragraph{The ``four quadrants'' of problem types}
Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
For further examples in the off-diagonal quadrants, see Appendix~\ref{app:omitted-examples}.

@@

\jessiet{This paragraph a little redundant}
The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
% This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss. 
%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}

\jessiet{Proposed paragraph about calibration to replace \S 2.2}
Given a target loss, calibration~\citep[Chapter 3]{steinwart2008support} is typically the tool used to study consistency.
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the first quadrant, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation to calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.

@@

\subsection{Property elicitation}\label{subsec:properties}
%\jessiet{Don't be too braggy}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
Intuitively, $p = \Pr[Y|X=x]$ is a conditional distribution, though the definition is also applied to point prediction settings.

@@

The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).

@@

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
Observe that this definition only makes sense given a target statistic with the introduction of consistency with respect to a statistic in Definition~\ref{def:consistent-prop}.

In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.

\begin{definition}[Convex Elicitation Complexity]
	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
\end{definition}
In particular, $\eliccvx(\prop{\ell}) \leq \ccdim(\ell)$ when restricting to minimizable surrogates ($\L$).

@@

In related work,
\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
%\btw{Bo: commented out what I felt was an unnecessary sentence}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

\jessiet{Simplify; merge with Sec 4?  Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.}

In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge that can be applied to all four quadrants.
For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.\jessiet{If we move calibration to the Appendix, this paragraph can be mostly removed}

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$, such that for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$, then we simply say $(L,\psi)$ is consistent.
\end{definition}

@@

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  %where $D_x = \Pr[Y|X=x]$.
  Suppose there is a set $\D$ such that, for all $p \in \P$, there is an $x \in \X$ and $D \in \D$ with a point mass on $x$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
\jessiet{Feels like this section got cut a lot for NeurIPS, but seems like some more narrative in this section might be helpful.}

>>>>

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\Lcvx}{\mathcal{L}^{\mathrm{cvx}}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\Scr}{\mathcal{S}}  % using this for the span of F_p - not sure if we want this to be parallel to the feasible subspace notation
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\section{Introduction}\label{sec:intro}
%supervised learning blah
Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task. \jessiet{Not quite what we want to say- can someone refine this?}
%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.

For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.

@@

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings. 
Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).

\paragraph{The ``four quadrants'' of problem types}
Above, we discuss a significant divergence in previous frameworks: the difference in constructing a surrogate given a \emph{target loss} and a \emph{target statistic}.
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
For further examples in quadrants 2 and 3, see Appendix~\ref{app:omitted-examples}.\jessiet{Don't actually have any Q3 examples in there at the moment}

@@

\jessiet{This paragraph a little redundant}
The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
which suggests property elicitation (see \S~\ref{subsec:properties}) is well-suited to study general lower bounds.
% This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions (Quadrant 1)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss, e.g. Quadrants 1 and 3. 
%\jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}

\jessiet{Proposed paragraph about calibration to replace \S 2.2}
As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration~\citep[Chapter3]{steinwart2008support}, which only applies when given a discrete target loss.
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in the Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex losses in $\L_d$.
\jessiet{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Moreover, we write $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ and continuous prediction spaces $\reals^d$.

@@

\subsection{Property elicitation}\label{subsec:properties}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only places characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p$ over $\Y$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
Intuitively, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

@@

\jessiet{I think it's okay to remove this paragraph completely.  We discuss \cite{agarwal2015consistent} other places.}
The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\reals^d$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\reals^d} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation is a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants (\S~\ref{sec:consis-implies-indir}).

@@

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
	Given a target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that there is a convex $L : \reals^d \times \Y \to \reals$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
A priori, this definition does not really make sense given a target statistic.
In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}

In the case of a target statistic $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.

\begin{definition}[Convex Elicitation Complexity]
	Given a target property $\gamma$, the \emph{convex elicitation complexity} $\eliccvx(\gamma)$ is the minimum dimension $d$ such that there is a $L \in \Lcvx_d$ indirectly eliciting $\gamma$.
\end{definition}
In particular, $\eliccvx(\prop{\ell}) \leq \conscvx(\ell)$ when restricting to minimizable surrogates ($\Lcvx$).

@@

\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
%\btw{Bo: commented out what I felt was an unnecessary sentence}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

%In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, and this is the first result to our knowledge relating consistency, calibration, and elicitation that can be applied to all four quadrants.
%For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
%For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration for settings in Quadrants 1 and 3.
%As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
%we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.
\jessiet{Removed a paragraph here about calibration and \cite{agarwal2015consistent} that is similar to a later discussion.}

We show indirect elicitation gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem 16]{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.

@@

\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are $\D$-consistent for a set $\D$ of distributions over $\X \times \Y$ with respect to a target loss $\ell$ if, for all $D \in \D$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
Given a set $\P \subseteq \simplex$, if for all distributions $p \in \P$, there exists a $D \in \D$ and $x \in \X$ such that $D$ has a point mass on $x$ and $p = D_x$, then we simply say $(L,\psi)$ is consistent.
\end{definition}

@@

\begin{definition}[Consistent: property]\label{def:consistent-prop}
	Suppose we are given a loss $L \in \L_d$, link function $\psi: \reals^d \to \R$, and property $\gamma:\P \toto \R$.
	Moreover, let $\propdis : \R \times \P \to \reals_+$ be any function satisfying $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
	We say $(L, \psi)$ is \emph{$(\propdis, \D)$-consistent with respect to} $\gamma$ if, for all $D \in \D$ and sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
    \E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
  \end{equation}
  %where $D_x = \Pr[Y|X=x]$.
  Suppose there is a set $\D$ such that, for all $p \in \P$, there is a $D \in \D$ with a point mass on some $x \in \X$ such that $p = D_x$ and a $\propdis$ satisfying the requirements above.
  In this case, if $(L,\psi)$ are $(\propdis,\D)$-consistent, we simply say the pair is consistent with respect to $\gamma$.
\end{definition}

@@

\section{Prediction Dimension of Consistent Convex Surrogates}\label{sec:char-convex}
We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex elicitation lower bounds.
The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.
